---
title: "R-Week2 HW-HJK"
author: "Hyun Jin Kim"
date: "July 27, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Assignment for Week 2

“n choose r” means n! / (( n – r)! * r!).ex: “5 choose 3” evaluates to 10. 
R has built in functions for choose() and factorial().
Your task is to write your own variation of the choose() function, that does not use either of these functions.
Your code should adhere to the style guidelines provided by Hadley Wickham in this week’s reading. 

1. Create loop for numerator for n! as well as a second loop for r!
2. create third controlling loop for (n-r)! as a function
3. Once 3 loops are created, use functions to create an uber function
```{r echo=TRUE}
apple <- function(n){
  y <- n
  x <- y-1
  while(x >=1){     #x is where you want the loop to break in this case
    y <- y * x
    x <- x - 1
  }
  return(y)}

nchooser <- function(n, r){
  return(apple(n) / (apple(n - r) * apple(r)))
  }

nchooser(5, 3)
```

```{r echo=TRUE}
nchooser(5,3) == choose(5,3)
nchooser(10,2) == choose (10,2)
